---
title: MSHS FTE Dashboard
author: Health System Operations
date: 'Publish Date: `r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
---

<style type="text/css">
div.main-container {
  max-width: 1760px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r, echo=F,warning=F,message=F,results='hide'}
source("Dashboard_Functions.R")
```
#### Reporting Period: `r rep`
#### Baseline Period: 12/22/2020 to 02/29/2020
## Mount Sinai Health System
### MSHS FTE Trend
```{r, echo=F,warning=F,message=F,fig.width=11}
system_total()
```
```{r, echo=F,warning=F,message=F}
system_table <- lapply(site_list, function(x) premier_sum_stats(data, x,service_lines))
system_table <- do.call(rbind, system_table) %>% arrange(Site)
system_table <- system_table %>% mutate(Site = "MSHS")  %>% ungroup() %>% group_by(Site) %>% summarise_at(vars(-group_cols()), sum)
system_kable(system_table)
```
### Site Comparison
```{r, echo=F,warning=F,message=F,fig.width=12}
site_total()
```
```{r, echo=F,warning=F,message=F}
site_table <- lapply(site_list, function(x) premier_sum_stats(data, x,service_lines))
site_table <- do.call(rbind, site_table) %>% arrange(Site)
system_kable(site_table)
```
### Nursing Comparison
```{r, echo=F,warning=F,message=F,fig.width=12}
nursing_total(nursing_service_lines)
```
```{r, echo=F,warning=F,message=F}
nursing_table <- lapply(site_list, function(x) premier_sum_stats(data, x,nursing_service_lines))
Service_Line_nursing <- do.call(rbind, nursing_table) %>% arrange(Site)
system_kable(Service_Line_nursing)
```
#### `r service_lines[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[1]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[1]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[1]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
#### `r service_lines[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[2]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[2]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[2]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
#### `r service_lines[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[3]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[3]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[3]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
#### `r service_lines[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[4]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[4]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[4]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
#### `r service_lines[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[5]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[5]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[5]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
#### `r service_lines[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[6]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[6]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[6]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
#### `r service_lines[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[7]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[7]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[7]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
### `r service_lines[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[8]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[8]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[8]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
### `r service_lines[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[9]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[9]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[9]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
### `r service_lines[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[10]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[10]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[10]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
### `r service_lines[[11]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[11]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[11]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[11]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
### `r service_lines[[12]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[12]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[12]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[12]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
### `r service_lines[[13]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[13]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[13]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[13]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
### `r service_lines[[14]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
graph_data(service_lines[[14]])
```
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(filter(data,SERVICE.LINE == service_lines[[14]])$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[14]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)%>% arrange(Site)
system_kable(Service_Line_table2)
```
## `r site_list[[1]]`
### `r MSH_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[1]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[1]])
```
### `r MSH_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[2]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[2]])
```
### `r MSH_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[3]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[3]])
```
### `r MSH_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[4]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[4]])
```
### `r MSH_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[5]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[5]])
```
### `r MSH_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[6]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[6]])
```
### `r MSH_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[7]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[7]])
```
### `r MSH_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[8]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[8]])
```
### `r MSH_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[9]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[9]])
```
### `r MSH_service_list[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[10]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[10]])
```
### `r MSH_service_list[[11]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[11]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[11]])
```
### `r MSH_service_list[[12]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[12]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[12]])
```
### `r MSH_service_list[[13]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[13]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[13]])
```
### `r MSH_service_list[[14]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[1]], service = MSH_service_list[[14]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[14]])
```
## `r site_list[[2]]`
### `r MSQ_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[2]], service = MSQ_service_list[[1]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[1]])
```
### `r MSQ_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[2]], service = MSQ_service_list[[2]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[2]])
```
### `r MSQ_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[2]], service = MSQ_service_list[[3]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[3]])
```
### `r MSQ_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[2]], service = MSQ_service_list[[4]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[4]])
```
### `r MSQ_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[2]], service = MSQ_service_list[[5]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[5]])
```
### `r MSQ_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[2]], service = MSQ_service_list[[6]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[6]])
```
### `r MSQ_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[2]], service = MSQ_service_list[[7]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[7]])
```
### `r MSQ_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[2]], service = MSQ_service_list[[8]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[8]])
```
## `r site_list[[3]]`
### `r MSBI_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[1]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[1]])
```
### `r MSBI_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[2]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[2]])
```
### `r MSBI_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[3]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[3]])
```
### `r MSBI_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[4]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[4]])
```
### `r MSBI_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[5]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[5]])
```
### `r MSBI_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[6]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[6]])
```
### `r MSBI_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[7]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[7]])
```
### `r MSBI_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[8]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[8]])
```
### `r MSBI_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[9]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[9]])
```
### `r MSBI_service_list[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[10]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[10]])
```
### `r MSBI_service_list[[11]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[3]], service = MSBI_service_list[[11]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[11]])
```
## `r site_list[[4]]`
### `r MSB_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[1]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[1]])
```
### `r MSB_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[2]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[2]])
```
### `r MSB_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[3]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[3]])
```
### `r MSB_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[4]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[4]])
```
### `r MSB_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[5]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[5]])
```
### `r MSB_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[6]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[6]])
```
### `r MSB_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[7]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[7]])
```
### `r MSB_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[8]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[8]])
```
### `r MSB_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[9]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[9]])
```
### `r MSB_service_list[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[4]], service = MSB_service_list[[10]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[10]])
```
## `r site_list[[5]]`
### `r MSW_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[1]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[1]])
```
### `r MSW_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[2]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[2]])
```
### `r MSW_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[3]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[3]])
```
### `r MSW_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[4]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[4]])
```
### `r MSW_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[5]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[5]])
```
### `r MSW_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[6]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[6]])
```
### `r MSW_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[7]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[7]])
```
### `r MSW_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[8]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[8]])
```
### `r MSW_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[9]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[9]])
```
### `r MSW_service_list[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[10]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[10]])
```
### `r MSW_service_list[[11]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[11]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[11]])
```
### `r MSW_service_list[[12]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[12]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[12]])
```
### `r MSW_service_list[[13]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[5]], service = MSW_service_list[[13]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[13]])
```
## `r site_list[[6]]`
### `r MSM_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[1]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[1]])
```
### `r MSM_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[2]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[2]])
```
### `r MSM_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[3]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[3]])
```
### `r MSM_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[4]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[4]])
```
### `r MSM_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[5]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[5]])
```
### `r MSM_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[6]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[6]])
```
### `r MSM_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[7]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[7]])
```
### `r MSM_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[8]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[8]])
```
### `r MSM_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[9]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[9]])
```
### `r MSM_service_list[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[10]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[10]])
```
### `r MSM_service_list[[11]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
service_line(hosp = site_list[[6]], service = MSM_service_list[[11]])
```
```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[11]])
```