---
title: MSHS FTE Dashboard
author: Health System Operations
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

<style type="text/css">
div.main-container {
  max-width: 1780px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r, echo=F,warning=F,message=F,results='hide'}
source("Dashboard_Functions.R")
```

## Mount Sinai Health System
### `r service_lines[[1]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[1]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[2]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[2]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[3]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[3]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[4]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[4]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[5]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[5]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[6]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[6]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[6]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[6]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[7]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[7]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[8]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[8]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[9]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[9]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[10]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[10]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[11]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[11]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[12]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[12]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
### `r service_lines[[13]]`
```{r, echo=F,warning=F,message=F}
# Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[13]]))
# Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
# kable(Service_Line_table2) %>%
#   kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
#   row_spec(0, background = "#212070", color = "white") %>%
#   row_spec(1:nrow(Service_Line_table2), color = "black") %>%
#   row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
#   column_spec(1,bold = T) #%>%
#   #collapse_rows(1)
```
### `r service_lines[[14]]`
```{r, echo=F,warning=F,message=F}
Service_Line_table2 <- lapply(unique(System_Summary$PAYROLL), function(x) premier_sum_stats(System_Summary,x, service_lines[[14]]))
Service_Line_table2 <- do.call(rbind, Service_Line_table2) %>% mutate(`Service Line` = NULL)
kable(Service_Line_table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Service_Line_table2), color = "black") %>%
  row_spec(0:nrow(Service_Line_table2), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) #%>%
  #collapse_rows(1)
```
## `r site_list[[1]]`
### `r MSH_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[1]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[1]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[2]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[2]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c") %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[3]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[3]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c") %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[4]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[4]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[5]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[5]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[6]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[6]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[7]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[7]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[8]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[8]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[9]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[9]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[10]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[10]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[11]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[11]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[11]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[12]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[12]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[12]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSH_service_list[[13]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[1]], service = MSH_service_list[[13]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[1]], service = MSH_service_list[[13]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
## `r site_list[[2]]`
### `r MSQ_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[2]], service = MSQ_service_list[[1]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[1]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSQ_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSQ_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[2]], service = MSQ_service_list[[2]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[2]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSQ_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSQ_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[2]], service = MSQ_service_list[[3]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[3]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSQ_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSQ_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[2]], service = MSQ_service_list[[4]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[4]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSQ_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSQ_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[2]], service = MSQ_service_list[[5]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[5]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSQ_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSQ_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[2]], service = MSQ_service_list[[6]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[6]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSQ_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSQ_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[2]], service = MSQ_service_list[[7]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[2]], service = MSQ_service_list[[7]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
## `r site_list[[3]]`
### `r MSBI_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[1]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[1]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[2]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[2]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[3]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[3]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[4]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[4]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[5]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[5]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[6]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[6]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[7]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[7]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[8]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[8]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[9]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[9]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[10]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[10]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSBI_service_list[[11]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[3]], service = MSBI_service_list[[11]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[3]], service = MSBI_service_list[[11]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
## `r site_list[[4]]`
### `r MSB_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[4]], service = MSB_service_list[[1]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[1]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSB_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[4]], service = MSB_service_list[[2]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[2]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSB_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[4]], service = MSB_service_list[[3]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[3]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSB_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[4]], service = MSB_service_list[[4]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[4]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSB_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[4]], service = MSB_service_list[[5]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[5]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSB_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[4]], service = MSB_service_list[[6]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[6]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSB_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[4]], service = MSB_service_list[[7]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[7]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSB_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[4]], service = MSB_service_list[[8]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[8]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSB_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[4]], service = MSB_service_list[[9]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[4]], service = MSB_service_list[[9]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
## `r site_list[[5]]`
### `r MSW_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[1]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[1]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[2]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[2]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[3]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[3]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[4]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[4]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[5]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[5]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[6]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[6]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[7]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[7]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[8]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[8]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[9]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[9]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[10]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[10]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[11]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[11]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[11]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSW_service_list[[12]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[5]], service = MSW_service_list[[12]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[5]], service = MSW_service_list[[12]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
## `r site_list[[6]]`
### `r MSM_service_list[[1]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[1]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[1]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSM_service_list[[2]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[2]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[2]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSM_service_list[[3]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[3]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[3]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSM_service_list[[4]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[4]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[4]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSM_service_list[[5]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[5]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[5]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSM_service_list[[6]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[6]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[6]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSM_service_list[[7]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[7]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[7]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSM_service_list[[8]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[8]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[8]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSM_service_list[[9]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[9]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[9]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```
### `r MSM_service_list[[10]]`
```{r, echo=F,warning=F,message=F,fig.width=12}
#lapply(MSH_service_list,function(x)service_line(hosp="MSH",service=x))
service_line(hosp = site_list[[6]], service = MSM_service_list[[10]])
```

```{r, echo=F,warning=F,message=F}
k(hosp = site_list[[6]], service = MSM_service_list[[10]])
kable(Ktable) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = T) %>%
  row_spec(0, background = "#212070", color = "white") %>%
  row_spec(1:nrow(Ktable), color = "black") %>%
  row_spec(0:nrow(Ktable), align = "c", font_size = 11) %>%
  column_spec(1,bold = T) %>%
  collapse_rows(1)
```